\section{Introduction}
\label{sec:intro}
\subsection{Motivation}
\label{subsec:motivation}
The problem of reconstructing a signal (or image) from (possibly) nonlinear observations is widely encountered in standard signal acquisition and imaging systems. Our focus in this paper is the problem of signal reconstruction from \textit{modulo} measurements, where the modulo operation with respect to a positive real valued parameter $R$ returns the (fractional) remainder after division by $R$. See Fig.~\ref{fig:orgmodop} for an illustration.

%The problem of reconstructing the signal from its modulo measurements, referred as \textit{modulo recovery problem} in the literature, can be formalized as follows.

Formally, we consider a high dimensional signal (or image) $\mb{x}^* \in \R^n$. We are given modulo measurements of $\mb{x^*}$, that is, for each measurement vector $\mb{a_i} \in \R^n$, we observe:
\begin{equation}
y_i=\mod(\langle \mathbf{a_i} \cdot \mathbf{x^*} \rangle,R)~~i = \{1,2,...,m\}, %\nonumber
\label{eq:modmeas0}
\end{equation} 
The task is to recover $\mb{x^*}$ using the modulo measurements $\mb{y}$ and knowledge the measurement matrix $\mathbf{A} = \left[\mathbf{a_1~a_2~...~a_m}\right]^\t$. %Here, $\mod(\cdot)$ is modulo operation with respect to the period $R$. 

%\begin{figure}[h]
%	\begin{center}
%		\begin{tikzpicture}[scale=0.7, every node/.style={scale=0.7}]
%		\draw[<->] (-4,0) -- (4,0) node[right] {$t$};
%		\draw[->] (0,-1) -- (0,4) node[above] {$f(t)$};
%		\draw[scale=0.5, dashed, thick] (0,4)--(7,4) node[right]{$R$};
%		\draw (1.5,-0.5) node(below) {$p_i = 0$};
%		\draw (-1.5,-0.5) node(below) {$p_i = 1$};
%		\draw (0,-1.5) node(right) {$f(t) = \mod(t,R)$};
%		\draw[scale=0.5,domain=-7:0,smooth,variable=\x,blue,thick] plot ({\x},{\x+4});
%		\draw[scale=0.5,domain=0:7,smooth,variable=\x,blue, thick]  plot ({\x},{\x});
%		\end{tikzpicture}
%	\end{center}
%	\caption{\emph{Modified modulo function for the given problem}}
%	\label{fig:modop}
%\end{figure}

% One such example is the classical problem of phase retrieval, which arises in numerous imaging applications including ptychography, diffraction imaging and astronomical imaging \cite{shechtman2015phase, maiden2009improved}. In such imaging systems, due to the limitations of the optical sensors, only the magnitude of the light rays can be measured but not the phase. As each linear observation losses its phase, the effective forward model can be expressed as a composition of nonlinear absolute value function with the linear observation function. Though the phase retrieval problem is challenging ill-posed inverse problem, it is well-studied in the literature and there exists multiple provably efficient algorithmic procedures to solve it in different settings \cite{Netrapalli2013,candes2013phaselift,candes2015phase,wang2016sparse}.

This specific form of signal recovery is gaining rapid interest in recent times. Recently, the use of a novel imaging sensor that wraps the data in a periodical manner  has been shown to overcome certain hardware limitations of typical imaging systems \cite{Bhandari,Zhao2015}. Many image acquisition systems suffer from the problem of limited dynamic range; however, real-world signals can contain a large range of intensity levels, and if tuned incorrectly, most intensity levels can lie in the saturation region of the sensors, causing loss of information through signal clipping. The problem gets amplified in the case of multiplexed linear imaging systems (such as compressive cameras or coded aperture systems), where required dynamic range is very high because of the fact that each linear measurement is a weighted aggregation of the original image intensity values. 

\begin{figure}[!t]
	\begin{center}
		\begin{tikzpicture}[scale=0.7]
			\draw[<->,thick] (-3,0)--(3,0) node[anchor=north]{$t$};
			\draw (0,0) node[anchor=north]{$0$};
			\draw (0,1.1) node[anchor=west] {$R$};
			\draw (1,0) node[anchor=north]{$R$};
			\draw (2,0) node[anchor=north] {$2R$};
			\draw (-1,0) node[anchor=north]{$-R$};
			\draw (-2,0) node[anchor=north] {$-2R$};
			%\draw [densely dotted,thick] (-2.5,1)--(3,1);
			\draw[->,thick] (0,0)--(0,2);
			\draw[] (2,1.5) node[anchor=west] {{$\mod(t,R)$}};
			\draw[thick] (1.6,1.5) -- (2,1.5);
			\draw[thick] (-2,0) --(-1,1)-| (-1,0) -- (0,1) -| (0,0) --(1,1)-| (1,0) -- (2,1) -| (2,0);
			\draw[densely dotted,thick] (2,0)--(2.5,0.5);
			\draw[densely dotted,thick] (-2,0)|-(-2,1) -- (-2.5,0.5);
			\end{tikzpicture}
	\end{center}
	\caption{\emph{Modulo operation with respect to $R$}}
	\label{fig:orgmodop}
\end{figure}


The standard solution to this issue is to improve sensor dynamic range via enhanced hardware; this, of course, can be expensive. An intriguing alternative is to deploy special digital \emph{modulo} sensors. As the name suggests, such a sensor wraps each signal measurement around a scalar parameter $R$ that reflects the dynamic range. However, this also makes the forward model \eqref{eq:modmeas0} highly nonlinear and the reconstruction problem highly ill-posed. The approach of~\cite{Bhandari,Zhao2015} resolves this problem by assuming \emph{overcomplete} observations, meaning that the number of measurements $m$ is higher than the ambient dimension $n$ of the signal itself. For the cases where $m$ and $n$ are large, this requirement puts a heavy burden on computation and storage. 

In contrast, our focus is on solving the the inverse problem~\eqref{eq:modmeas0} with very few number of samples, {i.e.}, we are interested in the case $m \ll n$. While this makes the problem even more ill-posed, we show that such a barrier can be avoided if we assume that the underlying signal obeys a certain low-dimensional structure. In this paper, we focus on the \emph{sparsity} assumption on the underlying signal, but our techniques could be extended to other signal structures. Further, for simplicity, we assume that our forward model is limited to only two periods of modulo operation: one in the positive half and one in the negative half as shown in the Fig.~\ref{fig:compare}(a). Such simplified version of the modulo function already inherits much of the challenging aspects of the original function. Intuitively, this simplification requires that the value of dynamic range parameter $R$ should be large enough so that all the measurements $\langle \mathbf{a_i} \cdot \mathbf{x^*} \rangle$ can be covered within the domain of operation of modulo function, \textit{i.e.}, $\langle \mathbf{a_i} \cdot \mathbf{x^*} \rangle \in [-R,R]~\forall i \in \{1,2,..,m\}$. 

%\subsection{Simplified setup}
% CH: this subsection is repetition of the above, probably not necessary
%\label{subsec:setup}
%The $\mod(\cdot,R)$ transfer function is many-to-one with infinite support. Thus, in this paper, we simplify our analysis by considering a simplified version of the modulo function that already inherits much of the challenging aspects of the original function. We consider a modified version that is truncated to only two periods of operation: one on the positive half and one in the negative half as shown in the Fig.~\ref{fig:compare}(a). %We also incorporate sparsity as a signal prior, thus capture the measurements in compressed sense, \textit{i.e.} $m<n$.
%Assume $\mathcal{X} \subseteq \R^n$ to be a given (known) subset in the data space, and consider a signal (or image) $\mb{x}^* \in \mathcal{X}$. We construct $\mathbf{A} = \left[\mathbf{a_1~a_2~...~a_m}\right]^\t$ with i.i.d. Gaussian entries and $m<n$. We aim to recover the original signal $\mb{x^*}\in \R^n$ from its compressed modulo measurements $y_i$, defined as:
%\begin{equation}
%y_i=\mod(\langle \mathbf{a_i} \cdot \mathbf{x^*} \rangle,R)~\textnormal{for}~i = \{1,2,...,m\},
%\label{eq:modmeas1}
%\end{equation} 
%where $\mod(\cdot)$ is modulo operation with respect to a fixed, real-valued parameter $R$. The primary assumption in our model is that the natural signal $\mathbf{x^*}$ is $s-$sparse in a chosen basis. 

%\begin{figure}[h]
%	\begin{center}
%		\begin{tikzpicture}[scale=0.7, every node/.style={scale=0.7}]
%		\draw[<->] (-4,0) -- (4,0) node[right] {$t$};
%		\draw[->] (0,-1) -- (0,4) node[above] {$f(t)$};
%		\draw[scale=0.5, dashed, thick] (0,4)--(7,4) node[right]{$R$};
%		\draw (1.5,-0.5) node(below) {$p_i = 0$};
%		\draw (-1.5,-0.5) node(below) {$p_i = 1$};
%		\draw (0,-1.5) node(right) {$f(t) = \mod(t,R)$};
%		\draw[scale=0.5,domain=-7:0,smooth,variable=\x,blue,thick] plot ({\x},{\x+4});
%		\draw[scale=0.5,domain=0:7,smooth,variable=\x,blue, thick]  plot ({\x},{\x});
%		\end{tikzpicture}
%	\end{center}
%	\caption{\emph{Modified modulo function for the given problem}}
%	\label{fig:modop}
%\end{figure}

\subsection{Our contributions}
In this paper, we propose a recovery algorithm for exact reconstruction of signals from modulo measurements of the form \eqref{eq:modmeas0}. We refer our algorithm as \emph{MoRAM}, short for \emph{Modulo Recovery using Alternating Minimization}. The key idea in our approach is to identify and draw parallels between modulo recovery and the problem of \emph{phase retrieval}. Indeed, this connection enables us to bring in algorithmic ideas from classical phase retrieval, which also helps in our analysis. 

Phase retrieval has its roots in several classical imaging problems, but has attracted renewed interest of late. There, we are given observations of the form:
\[
y_i= | \langle \mathbf{a_i} , \mathbf{x^*} \rangle|,~~i = 1, 2, \ldots, m,
\]
and are tasked with reconstructing $\mathbf{x^*}$.  While these two different class of problems appear different at face value, the common theme is the need of undoing the effect of a piecewise linear transfer function applied to the observations. See Fig.~\ref{fig:compare} for a comparison.
% While we deal with the modified version of modulo function with two periods in the case of modulo recovery, phase retrieval deals with absolute value function which is piece wise linear too. 
%Fig.~\ref{fig:compare} compares both the modulo ($f(t)$) and absolute value ($g(t)$) functions. 
Both the functions are identical to identity function in the positive half, but differs significantly in the negative half. Solving the phase retrieval problem is essentially equivalent to retrieving the phase ($\text{sign}\left(y_i\right)$) corresponding to each measurement $y_i$. However, the phase can take only two values: $1$ if $t \geq 0$, or $-1$ if $t < 0$. Along the same lines, for modulo recovery case, the challenge is to identify the bin-index $p$ for each measurement. %, and can take values $0$ if $t\geq 0$ or $1$ if $t<0$. 
Estimating the bin-index correctly lets us ``unravel'' the modulo transfer function, thereby enabling signal recovery.
\begin{figure}[h]
	\begin{center}
		\begin{tabular}{cc}
			\begin{tikzpicture}[scale=0.45, every node/.style={scale=0.7}]
			\draw[<->] (-4,0) -- (4,0) node[right] {$t$};
			\draw[->] (0,-1) -- (0,4);
			\draw[scale=0.5, dashed, blue, thick] (4,4)--(4,0) node[above right]{$R$};
			\draw (1.8,-0.5) node(below) {$\sgn(t) = -1$};
			\draw (-1.8,-0.5) node(below) {$\sgn(t) = 1$};
			\draw[scale=0.5,blue,thick] (1.5,6.5)--(2.5,6.5) node[right,black]{$f(t)$};
			%\draw[scale=0.5,dotted,red,ultra thick] (1.5,5.5)--(2.5,5.5) node[right,black]{$g(t)$};
			\draw (0,-1.5) node(right) {$f(t) = \mod(t,R)$};
			\draw[scale=0.5,domain=-4:0,smooth,variable=\x,blue, thick] plot ({\x},{\x+4});
			\draw[scale=0.5,domain=0:4,smooth,variable=\x,blue, thick]  plot ({\x},{\x});
			%\draw[scale=0.5,domain=0:7,smooth,variable=\x,red, ultra thick, dotted]  plot ({\x},{\x});
			%\draw[scale=0.5,domain=-7:0,smooth,variable=\x,red, ultra thick, dotted]  plot ({\x},{-\x});
			\end{tikzpicture} &
			
			\begin{tikzpicture}[scale=0.45, every node/.style={scale=0.7}]
			\draw[<->] (-4,0) -- (4,0) node[right] {$t$};
			\draw[->] (0,-1) -- (0,4);
			%\draw[scale=0.5, dashed, thick] (0,4)--(7,4) node[right]{$R$};
			\draw (1.8,-0.5) node(below) {$\sgn(t) = -1$};
			\draw (-1.8,-0.5) node(below) {$\sgn(t) = 1$};
			%\draw[scale=0.5,blue,ultra thick] (1.5,6.5)--(2.5,6.5) node[right,black]{$f(t)$};
			\draw[scale=0.5,red,thick] (1.5,6.5)--(2.5,6.5) node[right,black]{$g(t)$};
			\draw (0,-1.5) node(right) {$g(t)=\mathrm{abs}(t)$};
			%\draw[scale=0.5,domain=-7:0,smooth,variable=\x,blue, ultra thick] plot ({\x},{\x+4});
			%\draw[scale=0.5,domain=0:7,smooth,variable=\x,blue, ultra thick]  plot ({\x},{\x});
			\draw[scale=0.5,domain=0:4,smooth,variable=\x,red,thick]  plot ({\x},{\x});
			\draw[scale=0.5,domain=-4:0,smooth,variable=\x,red, thick]  plot ({\x},{-\x});
			\end{tikzpicture} \\
			(a) & (b)
		\end{tabular}
	\end{center}
	\caption{\emph{Comparison between (a) modulo function ($f(t) = \mod(t,R)$); and (b) absolute value function ($g(t) = \mathrm{abs}(t)$).}}
	\label{fig:compare}
\end{figure}

At the same time, several essential differences between the two problems restrict us from using algorithms for phase retrieval as-is for the modulo reconstruction problem. The absolute value function can be represented as a multiplicative transfer function (multiplication with the sign of the measurements), while the modulo function adds a constant value ($R$) to negative inputs. %Value of $p$ denotes whether the $R$ is added in the true measurement or not. It should be noted that the multiplication with $-1$ still preserves the magnitude information of the observations, while the additive process deforms the observation significantly, even more if the value of $R$ is higher. Additionally, the behavior of the modulo function is largely controlled by the value of the parameter $R$, while such parameter is non-existent in the case of absolute value function.
%Therefore, we can measure the effect of such nonlinearity by analyzing the error between true measurements and observed measurements for the negative half of the number-line. 
Therefore, estimation errors propagate very differently in the two cases. In the case of phase retrieval, a wrongly estimated phase induces an error that increases \emph{linearly} with the magnitude of each measurement. %Measurements closer to zero are less affected compared to measurements far from zero. In standard phase retrieval setup, as the true measurements are linear combination of the samples from the Gaussian distribution, resulting distribution of the true measurements follows the Gaussian curve, which makes most of the true measurements concentrate close to zero; lowering the severity of the corruption.
On the other hand, for modulo recovery problem, the error induced by an incorrect bin-index is $R$ (or larger), irrespective of the measurement. Therefore, existing algorithms for phase retrieval perform rather poorly for our problem (both in theory and practice). %Contrary to the case of phase retrieval, here the error is constant irrespective of magnitude of the true measurements. Even the true measurements lying very close to zero would experience the added error of $R$, and thus get severely affected. In the cases where $R$ is large, the magnitude of the additive corruption is way higher than the magnitude of the true measurement. Presence of such noise makes the recovery process very challenging.

We resolve this issue by making non-trivial modifications to existing phase retrieval algorithms that better exploit the structure of modulo reconstruction. We also provide analytical proofs for recoverying the underlying signal using our algorithm, and show that such a recovery can be performed using an (essentially) optimal number of observations, provided certain standard assumptions are met. To the best of our knowledge we are the first to pursue this type of approach for modulo recovery problems, distinguishing us from previous work~\cite{Zhao2015,Bhandari}. 

\subsection{Techniques}

%The proposed MoRAM algorithm is conceptually simple yet novel step in the direction of solving the problem of modulo recovery. Our work takes a fresh approach for solving the modulo recovery problem by borrowing the ideas from the well studied field of phase retrieval and compressive sensing. 
The basic approach in MoRAM is similar to the state-of-the-art phase retrieval approaches. As is the case with most of the non-convex phase retrieval algorithms, in the first step we identify a good initial guess $\mb{x^0}$ for our signal that lies relatively close to the true vector $\mb{x^*}$. A commonly used initialization technique for phase retrieval is \emph{spectral initialization} as described in \cite{Netrapalli2013}. However, that does not work in our case due to variedly different behavior of the modulo transfer function. %However, we observe that the initialization is easier to obtain if we have access to rather a small number of true measurements than having a large number of modulo measurements (corrupted by nonlinearity). 
We introduce a novel approach of measurement \emph{correcting} by comparing with typical histograms of Gaussian observations. Given access to such corrected measurements, $\mb{x^0}$ can be calculated simply by using a first-order estimator. This method is intuitive, yet provides % Our method of recalculating the partial number of true measurements from the set of modulo measurements is intuitive yet gives 
	a provable guarantee for getting a initial vector that is close to the true signal. 

Our second step is to refine this initial estimate to (ideally) provide the true underlying signal. Again, we follow an alternating-minimization (AltMin) approach inspired from the phase retrieval solutions~(\cite{Netrapalli2013}) that estimates the signal and the phase alternatively. However, as mentioned above, any estimation errors incurred in the first step induces fairly large additive errors (proportional to the dynamic range parameter $R$.) We resolve this issue by appealing to a \emph{robust} form of alternating minimization (specifically, the Justice Pursuit algorithm~\cite{Laska2009}). We prove that AltMin based on Justice Pursuit succeeds provided the number of wrongly estimated bin-indices in the beginning is a small fraction of the total number of measurements. This gives us a natural radius for initialization, and also leads to provable sample-complexity upper bounds.   % In particular,  we use the fact that justice pursuit algorithm manages to correct the corruption in bin-index values, provided the number of corrupted bin-indices is a fraction of total number of measurements. 

\subsection{Paper organization} 
The reminder of the paper is organized as follows. In section~\ref{sec:prior}, we briefly discuss the prior work. Sections~\ref{sec:prelim} contains notation and mathematical model used for our analysis. In section~\ref{sec:algo}, we introduce the MoRAM algorithm, and provide a theoretical analysis of its performance. We demonstrate the performance of our algorithm by providing series of numerical experiments in section~\ref{sec:exp}. Section~\ref{sec:disc} provides concluding remarks.